HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-19 draft/ms_v1_old.tex
New edits from Susan

% Commenting:
%% ------------------------------------------------------------------------------------ %%
\newcommand{\plan}[1]{\textcolor{blue} {\textbf{#1}}}
\newcommand{\todo}[1]{\textcolor{red} {\textbf{#1}}}
\newcommand{\song}[1]{\textcolor{cyan} {\textbf{#1}}}
\newcommand{\addref}{{\textcolor{red}{\textbf{REF}}}}
\newcommand{\term}[1]{\textbf{\texttt{#1}}}
\newcommand{\susan}[1]{\textcolor{magenta} {\textbf{#1}}}

@@

%% ------------------------------------------------------------------------------------ %%
\title{HSC Synthetic Pipeline I: Basic Design and Characterization of HSC
       Photometric Performance}

@@

   The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band
    survey using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
      At SSP's imaging depth \susan{quantify?}, it is challenging to achieve accurate,
    unbiased, and consistent photometry across all five bands. To improve data processing and achieve accurate photometric measurements, we have developed
   \synpipe{}, a \texttt{Python}-based, flexible framework
    that interfaces with the HSC data reduction pipeline (\hscpipe{}) to process data from the first public HSC--SSP data release. \susan{I expected to see something in the abstract that clarifies why this is Pipeline I; does this suggestion accomplish that?} We test  \synpipe{}
    performance by injecting synthetic objects into single-\texttt{visit} HSC images.
    We use coadded images in two Wide layer \tracts{} with representative
    seeing conditions to demonstrate  \synpipe{} implementation and to examine  \texttt{hscpipe}'s 
    general photometric performance.
    We find that uncertainties of HSC \forced{} PSF photometry for stars typically
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-7\% accuracy in the $i$-band). 
    For synthetic galaxies based on a single-\ser{} model, uncertainties of the
    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag to
    0.20 mag at $i{\sim} 25.2$ mag.
    Over the color and magnitude ranges used in the  \synpipe{} tests, we find that both 
    \forced{} PSF and \cmodel{} photometry provide unbiased color estimates that 
    are robust in different seeing conditions.
    We also notice a few issues in the current \hscpipe{} that are worth keeping
    in mind when using HSC data: 
    1) The degree to which an object is blended with others impacts the photometric 
    accuracy, especially for point sources.
    Highly blended objects tend to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) A relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects.
    3) The shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.

@@

    %% Background
    Wide-field, multi-band imaging surveys have stepped onto the central stage of
    modern astrophysics and cosmology over the past decade.
    They also have a bright future on many current and planned ambitious projects, such as the Large Synoptic Survey Telescope
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
    Telescope
    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
    and the \textit{Euclid} project
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}.
    Among many ongoing efforts, the Subaru Strategic Program
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
    uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
    the Subaru telescope, is the most efficient in terms of etendue.
    Together, these surveys will greatly help us test cosmological models, trace the
    evolution of galaxies, study the stellar structure of our Milky Way, and discover
    a large number of interesting transient objects.

    %% Challenges
    Before we can tackle any outstanding scientific questions, we must first learn
    how to handle the huge \susan{quantify? Or is "huge" a common descriptor for data in your field?} amount of data generated by these projects as well as achieve
    accurate photometric measurements of different types of objects.
    Data handling becomes increasingly challenging in the age of modern imaging
    surveys, in part due to variations and effects related to the cameras' charge-coupled devices (CCDs).
    The cameras are often made up of multiple
  CCDs, each with slightly different characteristics, and have
    large fields-of-view (FoV) over not perfectly flat focus planes.
    During  observation, the seeing and background conditions always show spatial
    and temporal variations across the FoV.
    The full-depletion, thick CCDs selected for the cameras enable long exposure times
    and excellent sensitivity in the red-end, but they often have the so-called
    ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that bright
    stars appear larger than they are.
   These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}).
    The multi-epoch, multi-band nature of the surveys also complicate
    data reduction because the scientist must pay special attention to
    image stacking, multi-band object detection, and measurement processes.
     Furthermore, as ongoing surveys reach to increasingly deeper surface brightness levels,
    the number of objects, especially faint objects, in a unit area, becomes much higher.
   In addition, it is much more common to observe objects that overlap each other at
    different levels (a phenomenon often referred to as ``blended'').
    These modern imaging survey challenges call for photometric measurement methods that are more powerful and precise than those
    used in previous, shallower surveys.

%% ------------------------------------------------------------------------------------ %%
    %% Reason
    The challenges are not merely technical details; their resolution is crucial
     to achieving the surveys' key scientific goals.
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
    is a powerful tool for measuring the large-scale distribution of dark matter and
    following its evolution.
    However, WL measurements critically depend on the ability to model PSF and measure the
    shape of background galaxies with high precision (e.g., \citealt{Mandelbaum2015}).
    The photometric redshift measurement (e.g., \citealt{Benitez2000, Bolzonella2000,
    Ilbert2009}) is fundamentally important for studying the evolution of galaxies,
    and the ``drop-out'' method is very useful in selecting high-redshift galaxies
    (e.g., \citealt{Steidel1996}).
    However, both of those methods are based on accurate multi-band photometric measurements.
    There are many other examples, but these are sufficient to demonstrate that we need to develop new frameworks
    to oversee the data reduction process of modern imaging surveys.
    Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
    Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}). \susan{Clarify why you mention the DES tools; e.g., does synpipe build on these tools? Do they demonstrate the effectiveness of developing new frameworks? Why are they insufficient for the HSC survey tasks?}

    %% Organization
  To test the data reduction quality of the HSC--SSP (hereafter referred to
    as the HSC survey) using synthetic objects, we have designed \synpipe{}, a \texttt{Python}-based
    software that
  is a flexible framework with many applications
    that can help future developments of the HSC data reduction pipeline as well as HSC Synthetic Pipeline I.
    Below, we briefly introduce the HSC survey and the current status of
    data reduction (Section \ref{sec:ssp}),  explain  \synpipe{}  design and implementation (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via
    straightforward tests (Section \ref{sec:test}) that focus on the general
    photometric quality for both synthetic stars and galaxies
    (Section \ref{sec:result}).
 We then summarize the work and discuss future developments in 
    Section \ref{sec:summary}.

   The  \synpipe{} code, along with basic documents and a few examples, is available
    on GitHub at: \url{https://github.com/dr_guangtou/synpipe}. \susan{Is this URL correct? I got a 404 Page Not Found when I tried it. I think the underscore needs to be replaced with a hyphen: https://github.com/dr-guangtou/synpipe}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of  \synpipe{} basic procedures.
        Grey  boxes indicate the required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects simulated
        images of synthetic objects onto a single-frame image. 
        We show an example CCD image with and without synthetic objects on it
        (highlighted by green circles).
        Red boxes depict the subsequent image coadding and multiband measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
        We show a small piece of coadded image with synthetic objects on it.
        The figure on the right side of the middle row shows the spatial relation
        between \tract{} (outlined by the black dashed lines; each small region
        is a \texttt{Patch}) and all the \visits{} that contribute to it. (Each \visit{} has a  unique color; each small region is the size
        of a CCD.)
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
\section{Hyper-Suprime Cam Subaru Strategic Program (HSC Survey)}
    \label{sec:ssp}

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2 m \susan{Style preference: space between value and m? Hyphenate?} Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (4 separated fields; ${\sim}27$ deg$^2$) and UltraDeep (2 separated
    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
     Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the HSC collaborators.

    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick CCDs: 112 for science and another 12 for guiding and focusing.
    The camera has a circular FoV with a 1.5 deg diameter.
    Each CCD contains 2048$\times$4096 pixels distributed in 4 amplifiers.
    The pixel size is equal to 0.168\asec{} on the sky.

   In February 2017, the HSC collaboration  released the first 1.7 years of data to the public (DR1;
    \citealt{HSCDR1})\footnote{\url{https://hsc_release.mtk.nao.ac.jp }}.\susan{URL is incorrect. Replace underscore with hyphen and add /doc: https://hsc-release.mtk.nao.ac.jp/doc/}
    For our work, we  focused on data from the Wide layer and the related major scientific goals, which include
    WL cosmology, galaxy evolution since $z{\sim}1$, and studies of galaxy clusters.
    The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
    6 different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator. 
        In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into 4
    dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
    uniform coverage.}; for the remaining 3 bands, 20 mins of exposure time and 6 dithers are
    used\footnote{Several 30 s exposures are taken to improve the dynamic range.}.
    The survey prioritizes the observations so that the $i$-band can have excellent
    seeing conditions to help make accurate WL shape measurements.
    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit. 
    \citealt{HSCDR1} provides details on the first data release and data status.
 .
%% ------------------------------------------------------------------------------------ %%

@@

    The HSC survey data are \susan{Style preference: data plural or singular? Later you use plural, and that's my preference, so I've changed the verb here.} currently reduced by \hscpipe{} \texttt{v4.0.5}, a
    version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010,
    Juric2015}), which is described in detail in Bosch\etal (in prep.).
    Since \synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{},  we briefly introduce the main steps below, along with
    a few key HSC/LSST terms.

@@

        \item \textbf{Single-\texttt{Visit~}Processing}:
            Each individual exposure is called a \term{Visit} and is assigned 
            an even integer.
            After initial data screening (in background, seeing, and transparency
            Furusawa\etal in prep.), \hscpipe{} detrends these data (subtraction
            of overscan, bias, and dark; flatfielding), generates variance and mask
            images, subtracts background, and provides initial astrometric and
            photometric calibrations.
            \textbf{\synpipe{} will use the spatially varying PSF models, photometric zeropoints, and the
            World Coordinate System (WCS; \citealt{WCS1, WCS2}) corrected for optical
            distortion.}.

        \item \textbf{Multi-\texttt{Visit~}Processing}:
            After single-\texttt{Visit~} processing, \hscpipe{}  warps and mosaics the reduced CCD images into
            much deeper \texttt{coadded} images while improving the astrometric and
            photometric calibrations via processes similar to the \"{u}ber-calibration
            in the Sloan Digital Sky Survey (SDSS) \citep{Padmanabhan2008}.
            \textbf{\synpipe{} will use these improved calibrations.}
            \hscpipe{} organizes these \texttt{coadded} images into equiareal \susan{or equal-area but not equi-area}
            rectangular regions, or \tracts{}, which are predefined as iso-latitude tessellations.
            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of
            sky, and adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.
            \textbf{The \tract{} and \texttt{Patch} are basic units to deal
            with HSC \texttt{coadded} images and \synpipe{} tests.}

        \item \textbf{Multi-band Measurements}:
            To achieve consistent photometry across all filters, \hscpipe{} first
            detects and deblends objects on \texttt{coadded} images in each band
            independently (the \unforced{} measurements).
            The collection of above-threshold pixels for each object is referred to as
          a  \texttt{footprint}.
           \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
            bands and then selects a reference band for each object based on its $S/N$ in
            each band (usually it is the $i$-band).
            With the centroids, shape, and other non-amplitude parameters fixed at the
            reference values, \hscpipe{} performs \forced{} photometry, which is
            optimized to generate accurate colors.

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain a variety of photometric
            information (see \citealt{HSCDR1} for details).
            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
            photometry.}
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources.
            Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
            the HSC \cmodel{}{} algorithm (described in Bosch\etal, in prep.) fits 
           each object's flux distribution using a combination of the de Vaucouleur
            profile and an exponential component that takes the PSF convolution into account.
            \cmodel{} is designed to yield accurate colors for galaxies.
            In addition, the star--galaxy separation task is performed based on the
            difference between the \texttt{psf} and \cmodel{}{} magnitudes.

@@

    DR1 data quality has been vetted in \citet{HSCDR1} via cross-checking
    with the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1
    imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the
    behaviors of the stellar sequence and the shape of the PSF models.
    Generally speaking, the PSF photometry is accurate to 1--2\% level, and the
    astrometry is accurate to ${\sim}10$ and 40 max internally and externally.

@@

%% ------------------------------------------------------------------------------------ %%
\subsection{ \synpipe{} Basic Design}
    \label{ssec:design}

     \hscpipe{} is a complex data reduction pipeline that still faces many challenges
    and is under active development. 
    Unlike most photometric pipelines on the market, it involves high-level reduction
    processes that produce not only deep \texttt{coadded} images but also a series of
    science-ready catalogs.
    To faithfully test \hscpipe{} and the related data products, we have designed an approach that ensures
    \synpipe{} satisfies a few basic standards:

@@

        \item \textbf{Realistic Images}:
            Instead of using the fully generative approach to simulate full HSC-like
            images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
            synthetic objects into the observed image so that all the realistic
            features of the real data (e.g., blended objects; proximity to bright
            objects, bleeding trails, other optical artifacts \susan{It's redundant to use etc. (or et al, which is incorrect here) with e.g.}) can be included
            in the test.
            The impact of these features can be important to any topic (e.g., WL analysis; stellar mass function of galaxies) that cares
            about the selection function and completeness of samples.
            In \synpipe{}, point source is simulated using the HSC PSF model,
            and a realistic galaxy model is created by the modular galaxy image
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\url{https://github.com/GalSim_developers/GalSim}} \susan{I got 404 Page Not Found when I tested the URL. Change underscore to hyphen: https://github.com/GalSim-developers/GalSim}.

        \item \textbf{Authentic Data Processing}:
            To follow the data reduction process as closely as possible, we choose to
            start from the single-\visit{} images instead of directly putting
            synthetic objects on the final \texttt{coadded} images
            (e.g., \citealt{Suchyta2016}).
            Through this approach, subtle effects like seeing differences among
            \visits{} and small errors in astrometric calibration can be taken
            into account.
            Every synthetic object will experience all the steps we would use for any real object: detection,
            deblending, stacking, and measurement.
            This can be important for challenging tasks like the WL measurements
            or the detection of high-$z$ galaxies.
            The only downside of this choice is that it will certainly slow down the
            test for \texttt{coadded} images because in this approach we need to inject synthetic objects
            into all the \visits{} that contribute to a \tract{}.

        \item \textbf{Flexible Capabilities}:
            We must make \synpipe{} flexible enough to be useful for HSC users with various scientific goals.
            We provide default catalogs to generate samples of synthetic stars
            and galaxies with realistic magnitude and color distributions along with
            tools to help the user work on HSC DR1 data; however, the user is allowed to be creative in terms of providing input catalogs and designing the tests.
             \synpipe{} is already being used in a wide range of
            scientific applications (see Section \ref{sec:summary} for details).

>>>>

% Commenting:
%% ------------------------------------------------------------------------------------ %%
\newcommand{\plan}[1]{\textcolor{blue} {\textbf{#1}}}
\newcommand{\todo}[1]{\textcolor{red} {\textbf{#1}}}
\newcommand{\song}[1]{\textcolor{cyan} {\textbf{#1}}}
\newcommand{\addref}{{\textcolor{red}{\textbf{REF}}}}
\newcommand{\term}[1]{\textbf{\texttt{#1}}}

@@

%% ------------------------------------------------------------------------------------ %%
\title{HSC Synthetic Pipeline I: Basic Design and Characterization of the
       Photometric Performance of HSC}

@@

    The Subaru Strategy Survey Program (SSP) is an ambitious wide-area, multi-band
    survey using the Hyper Suprime-Cam (HSC) on Subaru telescope.
    At the imaging depth of this survey, it becomes challenging to achieve accurate,
    unbiased, and consistent photometry across all five bands.
    In this work, we present \synpipe{}, a \texttt{Python}-based, flexible framework
    that interfaces with the HSC data reduction pipeline (\hscpipe{}) and test its
    performance via injecting synthetic objects to the single-\texttt{visit} HSC images.
    We use coadd images in two \tracts{} from the Wide layer with representative
    seeing conditions to demonstrate the implementation of \synpipe{} and examine the 
    general photometric performance of \texttt{hscpipe}.
    We find that the typical uncertainties of HSC \forced{} PSF photometry for stars
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-7\% accuracy in the $i$-band).
    For synthetic galaxies with single-\ser{} model, typical uncertainties of the
    forced \cmodel{} photometry range from 0.14 mag at $i{\sim}20.0$ mag to
    0.20 mag at $i{\sim} 25.2$ mag.
    Over the colors and magnitudes ranges used in these tests, we find that both 
    \forced{} PSF and \cmodel{} photometry provide unbiased estimates of colors that 
    are robust in different seeing conditions.
    Finally, we notice a few issues in the current \hscpipe{} that are worth keeping
    in mind when using HSC data: 
    1) the degree that a object is blended with others impacts the photometric 
    accuracy, especially for point sources.
    Highly blended object tends to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) a relative high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects.
    3) the shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.

@@

    %% Background
    Wide-field, multi-band imaging surveys have stepped onto the central stage of
    modern astrophysics and cosmology in the past decade.
    They also have a bright future as many ambitious projects are being carried out
    or planned, like the Large Synoptic Survey Telescope
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
    Telescope
    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
    and the \textit{Euclid} project
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}.
    Among many ongoing efforts, the Subaru Strategic Program
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}
    using the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
    the Subaru telescope is the most efficient one in term of Etendue.
    These surveys together will greatly help us test cosmological models, trace the
    evolution of galaxies, study the stellar structure of our Milky Way, and discover
    large number of interesting transient objects.

    %% Challenges
    Before we can tackle any outstanding scientific question, we first need to learn
    how to handle the huge amount of data generated by these projects, and achieve
    accurate photometric measurements of different types of objects.
    This target becomes increasingly challenging in the age of modern imaging
    surveys.
    The cameras that carry these surveys are often made up of multiple
    charge-coupled devices (CCDs) with slightly different characteristics and have
    large field-of-view (FoV) over not perfectly flat focus plane.
    During the observation, the seeing and background conditions always show spatial
    and temporal variations across the FoV.
    The full-depletion, thick CCD adopted by these cameras enables long exposure time
    and excellent sensitivity in the red-end, but they often have the so-called
    ``brighter-fatter'' effect (\citealt{Antilogus2014}) which means the size of bright
    stars are enlarged.
    All these issues make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g. \citealt{Schlafly2012}).
    In addition, the multi-epoch, multi-band nature of these surveys also complicate
    the data reduction as one needs to pay special attentions to the processes of
    image stacking, multi-band object detection and measurements.
    Furthermore, as ongoing surveys reach to much deeper surface brightness level,
    the number of objects in unit area, especially faint object, becomes much higher.
    Not only that, it is much more common to have objects that overlap each other at
    different levels (which is often referred to as ``blended'').
    Both situations ask for improved methods for photometric measurements than the ones
    used in previous, shallower surveys.

%% ------------------------------------------------------------------------------------ %%
    %% Reason
    These challenges mentioned above are not just technical details, they are crucial
    systematics to key scientific goals of these surveys.
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
    is a powerful tool to measure the large-scale distribution of dark matter and
    follow its evolution.
    The WL measurements critically depend on the ability to model PSF and measure the
    shape of background galaxies in high precision (e.g. \citealt{Mandelbaum2015}).
    Also, photometric redshift measurement (e.g. \citealt{Benitez2000, Bolzonella2000,
    Ilbert2009}) is fundamentally important for studying the evolution of galaxies;
    and the ``drop-out'' method is very useful in selecting high-redshift galaxies
    (e.g. \citealt{Steidel1996}).
    Both methods are based on accurate multi-band photometric measurements.
    The list goes on and on, but it becomes clear that we need to develop frameworks
    to oversee the data reduction process of modern imaging surveys.
    Several tools with similar goals have been developed (e.g. \citealt{Chang2015,
    Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}).

    %% Organization
    In this work, we present \synpipe{}, a \texttt{Python}-based
    software to test the data reduction quality of the HSC--SSP (will be referred to
    as the HSC survey) using synthetic objects.
    \synpipe{} is designed to be a flexible framework that has many applications
    and can help future developments of the HSC data reduction pipeline.
    Here, after briefly introducing the HSC survey and the current status of
    data reduction (Section \ref{sec:ssp}), we explain the design and implementation
    of \synpipe{} (Section \ref{sec:synpipe}), then we demonstrate its usage via
    straightforward tests (Section \ref{sec:test}) that focus on the general
    photometric quality for both synthetic stars and galaxies
    (Section \ref{sec:result}).
    Finally, we summary the work and discuss future developments in the
    Section \ref{sec:summary}.

    \synpipe{} code, along with basic documents and a few examples are available
    on GitHub at: \url{https://github.com/dr_guangtou/synpipe}.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the basic procedures of \synpipe{}.
        Grey color boxes indicate the required inputs at different stages.
        Blue box is for the \texttt{addFakes.py} step when \synpipe{} injects simulated
        images of synthetic objects onto single frame image.
        We show an example CCD image with and without synthetic objects on it
        (highlighted by green circles).
        Red boxes are for the following image coadding and multiband measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
        We show a small piece of coadd image with synthetic objects on it.
        The figure on the right side of the middle row shows the spatial relation
        between \tract{} (outlined by the black dashed lines; each small region
        is a \texttt{Patch}) and all the \visits{} that contribute to it
        (each \visit{} has its own unique color; each small region has the size
        of a CCD).
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
\section{Hyper-Suprime Cam Subaru Strategic Program}
    \label{sec:ssp}

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2m Subaru telescope,
    the ambitious HSC survey consists of three layers.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broadband
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (4 separated fields; ${\sim}27$ deg$^2$) and UltraDeep (2 separated
    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
    and employ slightly different survey strategy.
    Please refers to the survey description paper for more detailed information
    (Strauss\etal in prep.).

    The HSC camera (\citealt{Miyazaki2012}) is made up of 112 full-depletion thick CCDs
    for science and another 12 for guiding and focusing.
    It provides a circular FoV with 1.5 deg diameter.
    Each CCD contains 2048$\times$4096 pixels distributed in 4 amplifiers.
    The pixel size equals to 0.168\asec{} on the sky.

    The HSC collaboration just released the first 1.7 years of data to public (DR1;
    \citealt{HSCDR1})\footnote{\url{https://hsc_release.mtk.nao.ac.jp}}.
    For this work, we will focus on the Wide layer whose major scientific goals include
    WL cosmology, galaxy evolution since $z{\sim}1$, and studies of galaxy clusters.
    The current Wide layer includes ${\sim}108$ deg$^2$ of sky that are isolated in
    6 different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purpose.}.
    Most of these fields are close to the equator with the exception of the HECTOMAP
    field.
    In the Wide layer, the $g$ and $r$ bands have 10 mins exposure broken into 4
    dithers\footnote{Large, ${\sim}1/3$ of FoV dither pattern is used to ensure
    uniform coverage.}; for the rest 3 bands, 20 mins exposure time and 6 dithers are
    used\footnote{Several 30s exposures are taken to improve the dynamic range.}.
    The survey prioritizes the observations so that the $i$-band can have excellent
    seeing condition to help accurate shape measurements for WL.
    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit.
    For more details of the data status, please see the data release paper
    (\citealt{HSCDR1}).
%% ------------------------------------------------------------------------------------ %%

@@

    The HSC survey data is currently reduced by \hscpipe{} \texttt{v4.0.5}, a
    version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010,
    Juric2015}), which is described in detail in Bosch\etal (in prep.).
    Since \synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{}, here we briefly introduce the main steps along with
    a few key HSC/LSST terminologies.

@@

        \item \textbf{Single-\texttt{Visit~}Processing}:
            Each individual exposure is called a \term{Visit} and is assigned with
            an even integer.
            After initial data screening (in background, seeing, and transparency;
            Furusawa\etal in prep.), \hscpipe{} detrends these data (subtraction
            of overscan, bias, and dark; flatfielding), generates variance and mask
            images, subtracts background, and provides initial astrometric and
            photometric calibrations.
            \textbf{The spatially varying PSF models, photometric zeropoints, and the
            World Coordinate System (WCS; \citealt{WCS1, WCS2}) corrected for optical
            distortion will be used by \synpipe{}}.

        \item \textbf{Multi-\texttt{Visit~}Processing}:
            Then, \hscpipe{} then warps and mosaics these reduced CCD images into
            much deeper \texttt{coadd} images while improving the astrometric and
            photometric calibrations via processes similar to the \"{u}ber-calibration
            in SDSS \citep{Padmanabhan2008}.
            \textbf{\synpipe{} will use these improved calibrations.}
            \hscpipe{} organizes these \texttt{coadd} images into equi-area
            rectangular regions that are pre-defined as an iso-latitude tessellation
            and are referred to as \tract{}.
            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of
            sky, and adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.
            \textbf{The \tract{} and \texttt{Patch} are basic units to deal
            with HSC \texttt{coadd} images and \synpipe{} tests.}

        \item \textbf{Multi-band Measurements}:
            To achieve consistent photometry across all filters, \hscpipe{} first
            detects and deblends objects on \texttt{coadd} images in each band
            independently (the \unforced{} measurements).
            The above-threshold pixels for each object is referred to as
            \texttt{footprint}.
            Then, \hscpipe{} merges the \texttt{footprints} and flux peaks in different
            bands, and selects a reference band for each object based on its $S/N$ in
            each band (usually it is the $i$-band).
            With the centroids, shape, and other non-amplitude parameters fixed at the
            reference values, \hscpipe{} perform \forced{} photometry which is
            optimized to generate accurate colors.

        \item \textbf{HSC Photometry}:
            The multiband catalogs generated by \hscpipe{} contains various photometric
            information (see \citealt{HSCDR1} for details).
            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
            photometry.}
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources.
            Improved based on the SDSS version (\citealt{Lupton2001, Abazajian2004}),
            the HSC \cmodel{}{} algorithm (described in Bosch\etal in prep.) fits the
            flux distribution of each object using a combination of a de~Vaucouleur
            and an exponential component taking the PSF convolution into accounts.
            \cmodel{} is designed to yield accurate colors for galaxies.
            In addition, the star--galaxy separation task is performed based on the
            difference between the \texttt{psf} and \cmodel{}{} magnitudes.

@@

    The quality of the DR1 data have been vetted in \citet{HSCDR1} via cross-checking
    with the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1
    imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}), examining the
    behaviors of the stellar sequence and the shape of the PSF models.
    Generally speaking, the PSF photometry is accurate to 1--2\% level, and the
    astrometry is accurate to ${\sim}10$ and 40 mas internally and externally.

@@

%% ------------------------------------------------------------------------------------ %%
\subsection{Basic Design of \synpipe{}}
    \label{ssec:design}

    As summarized above and described in greater detail in Bosch\etal (in prep.),
    \hscpipe{} is a complex data reduction pipeline that still faces many challenges
    and is under active development.
    Unlike most photometric pipeline on the market, it involves high-level reduction
    processes that produce not only deep \texttt{coadd} images but also a series of
    science-ready catalogs.
    To faithfully test \hscpipe{} and these data products, we make sure the
    \synpipe{} satisfies a few basic standards:

@@

        \item \textbf{Realistic Images}:
            Instead of using the fully generative approach to simulate full HSC-like
            images from the ground up (e.g. \citealt{Chang2015}), \synpipe{} injects
            synthetic objects to the observed image so that all the realistic
            features of the real data (e.g. blended objects; approximity to bright
            object, bleeding trails, other optical artifacts \etal) can be included
            in the test.
            The impact of these features can be important to any topic that cares
            about the selection function and completeness of samples
            (e.g. WL analysis; stellar mass function of galaxies).
            In \synpipe{}, point source is simulated using the HSC PSF model,
            and realistic model of galaxy is modelled by the modular galaxy image
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\url{https://github.com/GalSim_developers/GalSim}}.

        \item \textbf{Authentic Data Processing}:
            To follow the data reduction process as close as possible, we choose to
            start from the single-\visit{} images instead of directly putting
            synthetic objects on the final \texttt{coadd} images
            (e.g. \citealt{Suchyta2016}).
            Through this approach, subtle effects like the seeing differences among
            \visits{} and small errors in astrometric calibration can be taken
            into accounts.
            All the synthetic objects will experience all the steps for detection,
            deblending, stacking, and measurement just like any real object.
            This can be important for challenging tasks like the WL measurements
            or the detection of high-$z$ galaxies.
            The only downside of this choice is that it will certainly slow down the
            test for \texttt{coadd} images as it needs to inject synthetic object
            to all the \visits{} that contribute to a \tract{}.

        \item \textbf{Flexible Capabilities}:
            To make \synpipe{} useful for HSC users with various scientific goals,
            we make sure it is flexible enough.
            Although we provide default catalogs to generate samples of synthetic stars
            and galaxies with realistic magnitude and color distributions along with
            tools to help work on data release of HSC survey, the user is allowed to
            be creative in term of providing input catalogs and design the tests.
            As we are speaking, \synpipe{} is being used in a wide range of
            scientific applications (see Section \ref{sec:summary} for details).
